Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-11 article/article.tex
Commit 2024-06-11 12:14

\usepackage{caption}
\usepackage{placeins}
\captionsetup{font=small}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

{\centering \includegraphics[width=1\linewidth]{../images/example-years-13}

@@

Our dataset, after the data selection processing, consists of 6144534
records of GHI measurements, of which \(1.764\,\%\) were identified as
CE events and \(0.036\,\%\) as ECE events. The highest recorded GHI due
to CE was \(1416.6\,\text{W}/\text{m}^2\) on 24~May 2007, and had the
maximum value of OIR at \(345.9\,\text{W}/\text{m}^2\). The relative
stronger CE event was \(49.7\,\%\) above the clear sky threshold, on
28~October 2016.

\hypertarget{long-term-trends}{%
\subsection{Long term trends}\label{long-term-trends}}

@@

{\centering \includegraphics[width=1\linewidth]{../images/P-energy-3}

\caption{Trends of the mean OIR per CE.}\label{fig:P-energy-mean}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{../images/P-energy-2}

\caption{Trend of yearly cloud enhancement occurrences.}\label{fig:P-energy-N}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{../images/P-energy-1}

\caption{Trend of the yearly excess energy due to CE over irradiance}\label{fig:P-energy-sum}
\end{figure}

>>>>

\usepackage{caption}
\usepackage{placeins}
\captionsetup{font=small}
\usepackage{subcaption}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

{\centering \includegraphics[width=1\linewidth]{../images/P-example-years-13}

@@

Following the application of the above discussed methodology to the
entire dataset (6.1 million one-minute GHI measurements), \(1.764\,\%\)
were identified as CE events and \(0.036\,\%\) as ECE events. The
highest recorded GHI due to CE was \(1416.6\,\text{W}/\text{m}^2\) on
24~May 2007, corresponding to OIR of \(345.9\,\text{W}/\text{m}^2\). The
stronger CE event of \(49.7\,\%\) above the clear sky threshold was
observed on 28~October 2016. In the following sections we are discussing
the long-term trends and variability of the CE events as well as of the
corresponding OIR and excess irradiation .

\hypertarget{long-term-trends}{%
\subsection{Long-term trends}\label{long-term-trends}}

@@

\begin{figure}[h!]
        {\centering 
            \subfloat[All skies.\label{fig:cusumnotrendmonthly-1}]
                {\includegraphics[width=\linewidth]{../images/P-energy-3} }\\
            \subfloat[Clear skies.\label{fig:cusumnotrendmonthly-2}]
                {\includegraphics[width=\linewidth]{../images/P-energy-2} }\\
            \subfloat[Cloudy skies.\label{fig:cusumnotrendmonthly-3}]
                {\includegraphics[width=\linewidth]{../images/P-energy-1} }
        }
    \caption{Time series for the period 1992 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OIR and (c) the yearly excess irradiation. The black lines represent the linear trends on the yearly data.}\label{fig:cusumnotrendmonthly}
\end{figure}
